How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-20 Paper/paper.tex
added repo link

Kragle, as well as all scraped programs and our analysis files are available via \todo{url} \todo{I do not think we need to describe the fields in the paper, but we need a good readme with the data (I can do that)}

>>>>

Kragle, as well as all scraped programs and our analysis files are available\footnote{\url{https://github.com/ScratchLover42/ICER-Data-Code}}.
